\class : Exam \psetnum

### 2022-05-17 531_stars/exam2/exam.tex
stars exam 2: part c numbers

\question{Calculate the minimum cooling rate required for the He-WD to reach the Chandrasekhar limit before any explosions occur.}

\answer{
    First, let's calculate the time until the WD reaches the Chandrasekhar limit
    \begin{equation}
        t_{\rm ch} = \frac{M_{\rm ch} - M_{\rm WD}}{\dot{M}_a}
    \end{equation}
    Now we can solve for the minimum cooling rate of the laser that keeps the temperature under the H-fusion ignition temperature in this amount of time.
    \begin{align}
        T_{\rm ign} &> (\dot{T}_{\rm accretion} - \dot{T}_{\rm laser}) t_{\rm Ch} \\
        \dot{T}_{\rm laser} &> \dot{T}_{\rm accretion} - \frac{T_{\rm ign}}{t_{\rm Ch}} \\
        \Aboxed{ \dot{T}_{\rm laser}&> \dot{M}_a \qty[\frac{2}{3 k_B} \frac{\mu m_H}{M_{\rm env}} \frac{G M_{\rm WD}}{R_{\rm WD}} - \frac{T_{\rm ign}}{M_{\rm ch} - M_{\rm WD}}] }
    \end{align}
}

>>>>

\question{Calculate the minimum cooling rate required for the WD to reach the Chandrasekhar limit before any explosions occur.

Plug in numbers for a He-WD with $M_{\rm WD} = 1.45 \unit{M_\odot}$, $M_{\rm env} = 10^{-5} \unit{M_\odot}$ and $\dot{M}_a = 10^{-8} \unit{M_\odot}{yr^{-1}}$}

\answer{
    First, let's calculate the time until the WD reaches the Chandrasekhar limit
    \begin{equation}
        t_{\rm ch} = \frac{M_{\rm ch} - M_{\rm WD}}{\dot{M}_a}
    \end{equation}
    Now we can solve for the minimum cooling rate of the laser that keeps the temperature under the H-fusion ignition temperature in this amount of time.
    \begin{align}
        T_{\rm ign} &> (\dot{T}_{\rm accretion} - \dot{T}_{\rm laser}) t_{\rm Ch} \\
        \dot{T}_{\rm laser} &> \dot{T}_{\rm accretion} - \frac{T_{\rm ign}}{t_{\rm Ch}} \\
        \Aboxed{ \dot{T}_{\rm laser}&> \dot{M}_a \qty[\frac{2}{3 k_B} \frac{\mu m_H}{M_{\rm env}} \frac{G M_{\rm WD}}{R_{\rm WD}} - \frac{T_{\rm ign}}{M_{\rm ch} - M_{\rm WD}}] }
    \end{align}
    Finally, we can start plugging numbers into this. Assuming the white dwarf follows the mass-radius relation then the radius is $R_{\rm WD} = 0.012 M_{\rm WD}^{-1/3}$. We additionally know that $T_{\rm ign} = 4 \times 10^6$ for H-fusion and $M_{\rm ch} = 1.46 \unit{M_\odot}, \mu = 2$ for a He-WD. Putting all of this into the equation above gives
    \begin{equation}
        \boxed{ \dot{T}_{\rm laser} \approx 10^6 \unit{K}{yr^{-1}}}
    \end{equation}
}
